From Freebase to Wikidata: The Great Migration

### 2015-10-15 paper.tex
PDF version of the reworked architecture diagram.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.7\columnwidth]{img/architecture.png}
    \caption{Primary Sources Tool architecture. The front-end is implemented in
      JavaScript and sends HTTP requests to the C++ back-end to retrieve and
      update entities or statements, which are stored in a~relational database.
      \todo{Create PDF version of the diagram, improve consistency of used terms}}
    \label{fig:architecture}
\end{figure}

>>>>

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.7\columnwidth]{img/architecture.pdf}
    \caption{Primary Sources Tool architecture. The front-end is implemented in
      JavaScript and sends HTTP requests to the C++ back-end to retrieve and
      update entities or statements, which are stored in a~relational database.}
    \label{fig:architecture}
    % Source: https://docs.google.com/a/google.com/drawings/d/1vKAftQVjrso907UtbMXnEOabXwQHDVyyz2ewxcqz3b0/edit?usp=sharing
\end{figure}
